---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE,
  include = TRUE
)
```

# skmisc (Shafayet Khan Miscellaneous) <a href="https://shafayetshafee.github.io/skmisc/"><img src="man/figures/logo.svg" align="right" height="139" alt="skmisc website" /></a>


[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg?style=flat)](https://choosealicense.com/licenses/mit/) 
[![CRAN status](https://www.r-pkg.org/badges/version/skmisc)](https://CRAN.R-project.org/package=skmisc)
[![Codecov test coverage](https://codecov.io/gh/shafayetShafee/skmisc/branch/main/graph/badge.svg)](https://app.codecov.io/gh/shafayetShafee/skmisc?branch=main)
[![R-CMD-check](https://github.com/shafayetShafee/skmisc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shafayetShafee/skmisc/actions/workflows/R-CMD-check.yaml)


The goal of `{skmisc}` is to provide some function that makes certain workflows easier. Currently, 
the only function that might be useful to anyone (who use Rmarkdown + LaTex) is
`skmisc::create_article_template`.

## Installation

`{skmisc}` is not on CRAN yet. You can install the development version of `{skmisc}` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("shafayetShafee/skmisc")
```

or, 

``` r
# install.packages("remotes")
remotes::install_github("shafayetShafee/skmisc")
```

## Example

### Create a Structured Article Template for a Journal Supported by `{rticles}`

Suppose you want to format your manuscript following the *Statistics in Medicine (SIM)* style 
using the R package [`rticles`](https://pkgs.rstudio.com/rticles/reference/article.html#sim-article).
The standard approach is:

``` r
rmarkdown::draft(
    "sim_article", 
    template = "sim", 
    package = "rticles",
    create_dir = TRUE,
    edit = FALSE
)
```

This creates a directory named `sim_article` in your working directory, containing all the 
files required for the *SIM* format. The structure looks like this:

``` bash
sim_article
├── bibfile.bib
├── Fonts
│   └── Stix
├── LETTERSP.STY
├── skeleton.log
├── sim_article.Rmd
├── WileyNJD-AMA.bst
└── WileyNJD-v5.cls
```

This works well, but the structure has one limitation: you must write your entire manuscript 
in a single Rmd file. However, I personally prefer keeping different major sections in separate 
Rmd files for better organization and modular editing.

That motivated the creation of the following function:

``` r
skmisc::create_article_template("sim")
```

Running this will create the directory `sim_article` with a more modular structure:

``` bash
sim_article
├── abstract.Rmd
├── bibfile.bib
├── Example.Rmd
├── Fonts
│   └── Stix
├── LETTERSP.STY
├── sections
│   ├── section01.Rmd
│   ├── section02.Rmd
│   ├── section03.Rmd
│   ├── section04.Rmd
│   └── section05.Rmd
├── sim_article.Rmd
├── skeleton.log
├── WileyNJD-AMA.bst
└── WileyNJD-v5.cls
```

In this layout, each major section lives in its own Rmd file, which the main file (`sim_article.Rmd`) 
includes as child documents. For example (non-essential YAML omitted):

<pre>
---
<..TRUNCATED..>
abstract: |
    &#96;r paste(readLines("abstract.Rmd"), collapse = "\n  ")&#96;
<..TRUNCATED..>
---

&#96;&#96;&#96;{r section01, child="sections/section01.Rmd"}
&#96;&#96;&#96;

&#96;&#96;&#96;{r section02, child="sections/section02.Rmd"}
&#96;&#96;&#96;

&#96;&#96;&#96;{r section03, child="sections/section03.Rmd"}
&#96;&#96;&#96;

&#96;&#96;&#96;{r section04, child="sections/section04.Rmd"}
&#96;&#96;&#96;

&#96;&#96;&#96;{r section05, child="sections/section05.Rmd"}
&#96;&#96;&#96;
</pre>

To check the formatted pdf out, you just knit this main `sim_article.Rmd` file. 
This structure allows you to keep your manuscript clean, organized, and modular.
Useful, innit? 🙂

> [!NOTE]
> `skmisc::create_article_template()` is a convenient wrapper around `rmarkdown::draft() `
> that lets you use any `{rticles}` journal format while working with multiple Rmd files.
> If you prefer the traditional single-file workflow, you should simply use `rmarkdown::draft()`
> with `{rticles}` directly.


### Converting the title of bib entries in a bib file to title case

```{r}
#| eval: true
library(skmisc)

bib_file <- system.file("extdata", "ref.bib", package = "skmisc")

# The title of each bib entry is in sentence case.
cat(readLines(bib_file), sep = "\n")

# converting the titles to title case.
tmp_output_file <- tempfile(fileext = ".bib")
bib_title_to_title_case(bib_file_path = bib_file, output_bib_file = tmp_output_file)

cat(readLines(tmp_output_file), sep = "\n")
```


## Code of Conduct

Please note that the skmisc project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
