---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# skmisc (Shafayet Khan Miscellaneous)

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg?style=flat)](https://choosealicense.com/licenses/mit/) 
[![CRAN status](https://www.r-pkg.org/badges/version/skmisc)](https://CRAN.R-project.org/package=skmisc)
[![Codecov test coverage](https://codecov.io/gh/shafayetShafee/skmisc/branch/main/graph/badge.svg)](https://app.codecov.io/gh/shafayetShafee/skmisc?branch=main)
[![R-CMD-check](https://github.com/shafayetShafee/skmisc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shafayetShafee/skmisc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `{skmisc}` is to provide some function that makes certain workflows easier. So far, the
only function that might be useful to anyone (who use Rmarkdown + LaTex) is `skmisc::create_article_template`.

## Installation

`{skmisc}` is not on CRAN yet. You can install the development version of `{skmisc}` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("shafayetShafee/skmisc")
```

or, 

``` r
# install.packages("remotes")
remotes::install_github("shafayetShafee/skmisc")
```

## Example

### Create a Structured Article Template for a Specified Journal Supported by `{rticles}`

``` r
create_article_template("arxiv")
```


### Converting the title of bib entries in a bib file to title case

```{r}
library(skmisc)

bib_file <- system.file("extdata", "ref.bib", package = "skmisc")

# The title of each bib entry is in sentence case.
cat(readLines(bib_file), sep = "\n")

# converting the titles to title case.
tmp_output_file <- tempfile(fileext = ".bib")
bib_title_to_title_case(bib_file_path = bib_file, output_bib_file = tmp_output_file)

cat(readLines(tmp_output_file), sep = "\n")
```


## Code of Conduct

Please note that the skmisc project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
