---
title: "Release Checklist"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

# Patch Release Workflow for skmisc

Run chunks interactively (eval = FALSE by default, since this is a checklist).

## 1. Pre-flight checks

```{r}
devtools::document()
devtools::test()
devtools::check()
```

## 2. Bump version (patch)

```{r}
usethis::use_version("patch")
```

This updates `DESCRIPTION` (Version field) and adds a new heading to `NEWS.md`.

## 3. Edit NEWS.md

Manually fill in bullet points describing changes under the new version
heading before continuing.

## 4. Rebuild README

```{r}
devtools::build_readme()
```

## 5. Update citation files

```{r}
cffr::cff_write()
usethis::use_citation()
```

## 6. Spell check & URL check

```{r}
devtools::spell_check()
urlchecker::url_check()
```

## 7. Final full check

```{r}
devtools::check(remote = TRUE, manual = TRUE)
```

## 8. Commit changes

```{bash}
git add DESCRIPTION NEWS.md README.md CITATION.cff inst/CITATION man/ R/
git commit -m "Patch vX.Y.Z: <summary>"
```

## 9. Tag and push

```{bash}
git tag vX.Y.Z
git push origin main --tags
```

## 10. Rebuild pkgdown site

```{r}
pkgdown::build_site()
```

## 11. CRAN submission (if applicable)

```{r}
devtools::release()
```
